Capstone Movielens Report

### 2025-12-14 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions description: `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1`, `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2`.

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $0$.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $0$.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

>>>>

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $1$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 1` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.

@@

This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $2$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.

@@

The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 2` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::
